### 2018-06-05 README.Rmd
fixed appveyor badge - #80

[![Travis Build Status](https://travis-ci.org/ropensci/visdat.svg?branch=master)](https://travis-ci.org/ropensci/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/visdat/master.svg)](https://codecov.io/github/ropensci/visdat?branch=master)

>>>>

[![Travis Build Status](https://travis-ci.org/ropensci/visdat.svg?branch=master)](https://travis-ci.org/ropensci/visdat)[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/ropensci/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/ropensci/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/ropensci/visdat/master.svg)](https://codecov.io/github/ropensci/visdat?branch=master)
